 
# Database with R

* [Data loading and manipulation](#data-loading-and-manipulation)
* [Output](#output)
    * [Table 1\. Proportion of pitches that are "called strikes" among all pitches outside the strikezone\.](#table-1-proportion-of-pitches-that-are-called-strikes-among-all-pitches-outside-the-strikezone)
    * [Table 2\. Proportion of pitches that are "called strikes" among all pitches outside the strikezone by count\.](#table-2-proportion-of-pitches-that-are-called-strikes-among-all-pitches-outside-the-strikezone-by-count)
    * [Figure 1\. Proportion of pitches that are "called strikes" among all pitches outside the strikezone by count\.](#figure-1-proportion-of-pitches-that-are-called-strikes-among-all-pitches-outside-the-strikezone-by-count)

### Data loading and manipulation

* Load webscraped baseball PITCHf/x data to SQLite database. 
* Extract count, called strike, pitch information, merge with umpire dataset.

```{r}
#setup
library(knitr)
opts_chunk$set(tidy = TRUE, cache=TRUE, autodep=TRUE, message=FALSE)
```


```{r, results = 'hide'}
library(pitchRx)
library(dplyr)
library(RSQLite)
library(DBI)
library(ggplot2)

db <- src_sqlite("pitchfx.sqlite3", create = T)

files <- c("inning/inning_all.xml", "players.xml")
scrape(start = "2013-06-01", end = "2013-06-01", suffix = files, connect = db$con)
# dat2 <- scrape(start = "2013-06-01", end = "2013-06-01", suffix = files)

#db <- src_sqlite("pitchfx.sqlite3")

pitch_dt <- tbl(db, "pitch")
umpire_dt <- tbl(db, "umpire")
atbat_dt <- tbl(db, "atbat")
#pitch2_dt <- dat2[["pitch"]]
#umpire_dt <- dat[["umpire"]]


atbat <- select(atbat_dt, gameday_link, num, stand, p_throws, inning, pitcher_name)

pitch_umpire <- 
    umpire_dt %>%
    filter(position == "home") %>%
    inner_join(pitch_dt, by ="gameday_link") %>%
    distinct()

#outside_zone
out_zn <- pitch_umpire %>%
    filter((px < -.85 | px > .85 | pz < sz_bot | pz > sz_top), 
           des %in% c("Called Strike", "Ball")) %>%
    mutate(cs_ind = as.numeric(des == "Called Strike")) %>%
    select(position, name, id.x, des, cs_ind, px, pz, sz_top, sz_bot, num, count, gameday_link) %>%
    collect()

#proportion of pitches that are "called strikes" among all pitches outside the strikezone.

cs_out_zn_all <-
    out_zn %>%
    summarize(sum = sum(cs_ind), n = n()) %>%
    collect() %>%
    mutate(cs_out_zn = sum / n)

names(cs_out_zn_all) <- c("# Called Strikes","# Pitches","Called strikes %")

cs_out_zn_count <-
    out_zn %>%
    group_by(count) %>%
    summarize(sum = sum(cs_ind), n = n()) %>%
    collect() %>%
    mutate(cs_out_zn = sum / n)

figure1 <- ggplot(data=cs_out_zn_count,aes(x=count,y=cs_out_zn)) + geom_point(color = "blue", size = 4) + ylab("Probalilities by count") + theme_bw()

names(cs_out_zn_count) <- c("Count","# Called Strikes","# Pitches","Called strikes %")
```


### Output

#### Table 1. Proportion of pitches that are "called strikes" among all pitches outside the strikezone.
```{r, echo = F}
kable(cs_out_zn_all)
```

#### Table 2. Proportion of pitches that are "called strikes" among all pitches outside the strikezone by count.
```{r, echo = F}
kable(cs_out_zn_count)
```

#### Figure 1. Proportion of pitches that are "called strikes" among all pitches outside the strikezone by count.

```{r, echo = F}
figure1
```
